### 2020-12-23 docs/manuscript/PLOS-MSc-Thesis.tex
Remove trailing whitespaces and change abundance vs complexity fig to log
Delete paragraph about GRNs reaching quickly the steady state

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/abundance-vs-complexity-index}
 \caption{\bf Scatter plot of Abundance vs. Complexity index.}
 Each point in the plot represents one of the 714 network topologies.
 \label{fig:ab-comp}
\end{figure}

Spatiotemporal expression profiles showed that all GRNs reached a steady state
expression profile before $t = 250$ and most of them indeed reached the steady
state before $t = 150$ (Fig~\ref{fig:profile}).

>>>>

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/abundance-vs-complexity-index-log}
 \caption{\bf Scatter plot of Abundance vs. Complexity index.}
 Each point in the plot represents one of the 714 network topologies.
 \label{fig:ab-comp}
\end{figure}
